%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Technical Documentation Writer} % Job title
{OpenIndiana} % Organization
{\href{https://github.com/OpenIndiana/oi-docs}{github.com/OpenIndiana/oi-docs}} % Location
{2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item{Recommended the switch from \href{https://www.atlassian.com/software/confluence}{Alassian Confluence Wiki} to \href{http://www.mkdocs.org/}{MkDocs} to reduce project complexity.}
\item {Helped to convert documentation from \href{https://www.atlassian.com/software/confluence}{Alassian Confluence Wiki} to \href{http://www.mkdocs.org/}{MkDocs}.}
\item {Contributed some of my own documentation from a past project.}
\item {Helped setup and test \href{https://travis-ci.org/}{Travis CI}, a continous integration service.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Volunteer} % Job title
{CyberTech} % Organization
{Norwich, NY, USA} % Location
{Dec. 2014 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Fixed various issues with software and hardware.}
\item {Conversed with clients to help diagnose issue.}
\item {Explained things to clients in a way they could understand.}
\item {Have gone on house and bussiness calls.}
\item {Endorsed the use of Open Source software.}
\item {Introduced Linux as a daily driver, and great debugging tool.}
\item {Helped setup network infrastructure to improve the repair workflow.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Community member} % Job title
{iPXE} % Organization
{\href{http://ipxe.org/}{ipxe.org}} % Location
{2015 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {\href{https://git.ipxe.org/ipxe.git/commit/f6e1da5cbf70a372f2b622c8021c98503cab8323}{Helped to debug and test a build issue on Ubuntu.}}
\item {I try to answer the questions of community members in the \#ipxe channel on freenode.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Community Member} % Job title
{Linux Distro Community} % Organization
{\href{https://www.linuxdistrocommunity.com/}{linuxdistrocommunity.com}} % Location
{2014 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Been an active community member.}
\item {Helped other users of the community with issues they were facing.}
\item {Was a staff moderator for Mumble.} 
\end{cvitems}
}

%------------------------------------------------

\cventry
{Community member} % Job title
{Nixheads} % Organization
{\href{http://nixheads.co.uk/}{nixheads.co.uk}} % Location
{2015 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Helped establish the \href{https://github.com/nixheads}{nixheads github organization}.}
\item {Was an early community member.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Member} % Job title
{Github} % Organization
{\href{https://github.com/AdrianKoshka/}{github.com/AdrianKoshka/}} % Location
{Sep. 7 2014 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Maintain my own Open Source repositories}
\item {Contributed to other Open Source projects.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
