\section{Introduction}
\paragraph{}
My name is Theodore Se\'{a}n Tubbs, and I am a student of DCMO BOCES, my
home-school is Norwich High School of Norwich, NY. Throughout my schooling
career I've always been passionate about learning things that interest and
intrigue me, Whether that be science, social studies, IT, graphic design, or
anything else.

\subsection{Why I chose DCMO BOCES}

\subsubsection{My First Year}
\paragraph{}
Initially I decided to take the Computer Repair \& Networking Technology course
at DCMO BOCES, I took this course in hopes of learning something new, as I had
10 years experience in IT previously. Though I ended up being unsatisfied with
the course, learning nothing, and bickering with the intructor over litle petty
things because of his authoritarianess. Though halfway through the year the
instructor left due to medical issues, the class pretty much fell into ruins
and I almost wasted half a year learning nothing.

\paragraph{}
Though I ended up dabbling with the graphics design course thanks to a group of
friends I had taking the course. Though I didn't end up doing much that half
year I decided I might switch my course to graphics design.

\subsubsection{My Second Year}
\paragraph{}
Upon Arrival back to my computer tech class, the instructor was back, and
everyone was informed because of a few cheaters everyone's certification had
been revoked by CISCO (overkill in my opinion). This was pretty much the last
straw for me, I had wasted half a year learning things I already knew, and the
other half not learning much at all.

\paragraph{}
This is when I switched to the graphics design course. My reasoning for
switching to the graphics design course is as follows:

\begin{itemize}
	\item {I had previous experience and knowledge in IT which gave me a leg up.}
	\item {I was fairly easily able to adapt to the classroom environment.}
	\item {I am fairly quick to adapt to new things (partially my IT experience).}
	\item {IT and media are two industries that are fairly intertwined.}
\end{itemize}

\paragraph{}

Some interests I have in the media field are:

\begin{itemize}
	\item {Audio Engineering.}
	\item {Cinematography.}
	\item {Colour grading.}
	\item {Photography.}
	\item {Special effects.}
\end{itemize}

Overall I'd say I have adapted well to the graphics design course and am much happier.

\subsection{My Passion about learning}

\paragraph{}
As I said above, I've always been quite passionate about learning, and I'd say
the amount of things I've learned since enteresting highschool has exploded
rapidly. A short list of things I've learned since highschool are:

\begin{itemize}
	\item {\href{https://www.gnu.org/software/bash/}{Bash}, a shell scripting language with a plethora of uses, such as:}
		\begin{itemize}
			\item Automation.
			\item Efficiently getting small and large tasks done.
			\item And many other things.
		\end{itemize}
	\item {\href{https://git-scm.com/}{Git}, a free and open source version control system.}
		\begin{itemize}
			\item Git is used as the version control software in a mind-boggling amonut of open-source projects
			\item The repository for the source-code of my NTHS papers are a git repository
			\item Version control is a powerful tool in documentation, and software development among other things.
		\end{itemize}
	\item {\href{https://www.latex-project.org/}{\LaTeX{}}, an advanced markup language for creating documents, presentations, and anything inbetween.}
		\begin{itemize}
			\item I use \LaTeX{} for most of my school papers and presentations.
			\item The papers/presentations I've done in \LaTeX{} are open-source, so you can get the code.
			\item This document itself it written in \LaTeX{}.
		\end{itemize}
	\item {\href{https://guides.github.com/features/mastering-markdown/}{Markdown}, a more lightweight markup langauage for documentation}
	\item { \href{http://www.mkdocs.org/}{MkDocs}, a static site generater geard towards technical documentation projects.}
		\begin{itemize}
			\item This is one of the languages used in MkDocs
			\item This language is widely used in OpenSource projects
		\end{itemize}
	\item {Various distrobutions of the GNU/Linux Operating System.}
		\begin{itemize}
			\item {\href{https://www.centos.org/}{Centos}}
			\item {\href{https://www.debian.org/}{Debian}}
			\item {\href{https://getfedora.org/}{Fedora}}
			\item {\href{https://www.opensuse.org/}{OpenSUSE Leap}}
			\item {\href{https://www.ubuntu.com/}{Ubuntu}}
		\end{itemize}
\end{itemize}

Here is a list of things I've started to learn ever since taking the graphics design course:

\begin{itemize}
	\item Colour grading
	\item Special Effects
	\item The principles of design
\end{itemize}

While this list is alot shorter, we have not gotten into specialization yet,
and it is quite early in the year. I'm sure my ability is easily adapt to 
ever-changing environments, and easily learning a plethora of things a variety
of fields will surely help me in the future.

\section{Conclusion}
\subsection{Why I should be inducted into the NTHS}

\paragraph{}
I think my fervent passion for learning, and the broad array of things I already 
know are a great foundation, and NTHS would only help me build upon that
foundation. Going straight into the workforce and having the technical
endorsement would certainly give me a leg up on most people in my local area.
